---
output:
  pagedown::html_paged:
    css: ["styles.css"]
---

```{r setup, include=FALSE}
library(yaml)
library(readr)

`%||%` <- function(a, b) {
  if (!is.null(a)) a else b
}

info <- yaml::read_yaml("data/info.yml")
education <- readr::read_csv("data/education.csv", show_col_types = FALSE)
research <- readr::read_csv("data/research_experience.csv", show_col_types = FALSE)
teaching <- readr::read_csv("data/teaching_experience.csv", show_col_types = FALSE)
collective <- readr::read_csv("data/collective_engagement.csv", show_col_types = FALSE)
publications <- readr::read_csv("data/publications.csv", show_col_types = FALSE)
languages <- readr::read_csv("data/languages.csv", show_col_types = FALSE)
skills <- yaml::read_yaml("data/skills.yml")

render_entries <- function(df, title_col = NULL) {
  clean_val <- function(x) {
    if (is.null(x) || is.na(x) || trimws(x) == "") "" else trimws(x)
  }

  for (i in seq_len(nrow(df))) {
    title_value <- if (!is.null(title_col)) {
      clean_val(df[[title_col]][i])
    } else if ("role" %in% names(df)) {
      clean_val(df$role[i])
    } else if ("degree" %in% names(df)) {
      clean_val(df$degree[i])
    } else {
      ""
    }

    institution <- if ("institution" %in% names(df)) clean_val(df$institution[i]) else ""
    location <- if ("location" %in% names(df)) clean_val(df$location[i]) else ""
    subtitle <- if ("subtitle" %in% names(df)) clean_val(df$subtitle[i]) else ""
    details <- if ("details" %in% names(df)) clean_val(df$details[i]) else ""
    dates <- if ("dates" %in% names(df)) clean_val(df$dates[i]) else ""

    subtitle_parts <- c(institution, location)
    subtitle_line <- paste(subtitle_parts[subtitle_parts != ""], collapse = ", ")

    cat('<div class="entry">')
    cat('<div class="entry-header">')
    cat(sprintf('<div class="entry-title">%s</div>', title_value))
    cat(sprintf('<div class="entry-dates">%s</div>', dates))
    cat('</div>')

    if (subtitle_line != "") {
      cat(sprintf('<div class="entry-subtitle">%s</div>', subtitle_line))
    }

    if (subtitle != "") {
      cat(sprintf('<div class="entry-details"><em>%s</em></div>', subtitle))
    }

    if (details != "") {
      cat(sprintf('<div class="entry-details">%s</div>', details))
    }

    cat('</div>')
  }
}
```

# `r info$name`

```{r contact, results='asis', echo=FALSE}
cat('<div class="contact-info">')
cat(info$location, '<br>')
cat(sprintf('<a href="mailto:%s">%s</a><br>', info$emails[[1]], info$emails[[1]]))
cat(sprintf('<a href="mailto:%s">%s</a><br>', info$emails[[2]], info$emails[[2]]))
cat(sprintf('<a href="%s">LinkedIn</a> | ', info$links$LinkedIn))
cat(sprintf('<a href="%s">GitHub</a> | ', info$links$GitHub))
cat(sprintf('<a href="%s">ORCID</a>', info$links$ORCID))
cat('</div>')
```

## Academic Orientation

`r info$academic_orientation`

## Research Interests

`r paste(info$research_interests, collapse = "; ")`

## Education

```{r education_section, results='asis', echo=FALSE}
render_entries(education, title_col = "degree")
```

## Research Experience

```{r research_section, results='asis', echo=FALSE}
render_entries(research, title_col = "role")
```

## Teaching Experience

```{r teaching_section, results='asis', echo=FALSE}
render_entries(teaching, title_col = "role")
```

## Collective Engagement and Community-Based Work

```{r collective_section, results='asis', echo=FALSE}
render_entries(collective, title_col = "role")
```

## Publications

```{r publications_section, results='asis', echo=FALSE}
cat('<ul class="pub-list">')
for (i in seq_len(nrow(publications))) {
  cat(sprintf('<li>%s</li>', publications$citation[i]))
}
cat('</ul>')
```

## Methods and Technical Skills

**Qualitative and Mixed Methods:** `r skills$qualitative_and_mixed_methods`

**Quantitative Methods and Data:** `r skills$quantitative_and_data`

**Research Production:** `r skills$research_production`

**Digital and Organizational Tools:** `r skills$digital_and_organizational_tools`

## Languages

```{r languages_section, results='asis', echo=FALSE}
cat('<ul class="languages-list">')
for (i in seq_len(nrow(languages))) {
  cat(sprintf('<li><strong>%s:</strong> %s</li>', languages$language[i], languages$level[i]))
}
cat('</ul>')
```